Formalizing the Edmonds-Karp Algorithm

### 2016-03-02 paper/root.tex
Added TODOs to latex file

In reference books, it is a convention to use pseudocodes for presenting the algorithms. The abstract version of the algorithm has a clean correctness proof as it only captures the idea behind the algorithm and leaves out the implementation details. We present the Ford-Fulkerson method using the syntax of Autoref~\cite{La13} tool which is quite similar to pseudocode of the algorithm:
\Snippet{ford_fulkerson_algo}

>>>>

In reference books, it is a convention to use pseudocodes for presenting the algorithms. The abstract version of the algorithm has a clean correctness proof as it only captures the idea behind the algorithm and leaves out the implementation details. We present the Ford-Fulkerson method using the syntax of (TODO: here I mention autoref again, I was not aware that we are not using it anymore. So please correct all the references that I made to autoref tool) Autoref~\cite{La13} tool which is quite similar to pseudocode of the algorithm:
\Snippet{ford_fulkerson_algo}
